### 2025-04-08 LabelStyles/SoS-skeleton-Det.Rmd
working on vignette example

```{r load data}
data <- read.csv('../data/processed/cleaned_data.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE `r data$Project_name`}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
\endgroup

@@

\vspace*{\fill}
\begingroup
`r collection_writer(data)`. `r writer_fide(data)`
\endgroup

>>>>

```{r load data}
data <- read.csv('SoS-ExampleCollection.csv') |>
  dplyr::mutate(
    Collection_number = as.numeric(Collection_number), 
    Coordinate_Uncertainty = '+/- 5m') |>
  dplyr::filter(Collection_number == params$Collection_number)
```

\begin{center}
\textbf{\LARGE Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
`r writer_fide(data)`
\endgroup

@@

\vspace*{\fill}
\begingroup
`r collection_writer(data)`.
\endgroup

\begin{center}
{\footnotesize Collected under the auspices of the Bureau of Land Management}
\end{center}

### 2025-04-08 LabelStyles/SoS-skeleton-familyLeft.Rmd
working on vignette example

\begin{center}
\textbf{\LARGE Seeds of Success}
\end{center}
\begin{flushright}
\uppercase{`r data$Family`}
\end{flushright}
\begingroup
\large
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\normalsize
\endgroup

>>>>

\begin{center}
\textbf{\LARGE `r data$Project_name`}
\end{center}
\large
\uppercase{`r data$Family`}  
\begingroup
`r writer(paste(data$Genus, data$Epithet), italics = TRUE)` `r writer(data$Binomial_authority)` `r writer(data$Infrarank)` `r  writer(data$Infraspecies, italics = TRUE)` `r writer(data$Infraspecific_authority)`  
\endgroup
\normalsize
